Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-07 ba_resubmit/response_to_reviewers2.tex

\section{AE Comments}

\pointRaised{AE}{I must add that reading the paper still feels like a chore, in part because the notation is so heavy, which may be hard to avoid, but also, in part, because some wording choices make certain sentences hard to parse, which can certainly be improved.}

\reply{We agree that our notation is at times cumbersome. We have made several efforts to simplify notation in this revision.

\begin{itemize}
	\item Instead of referring to files as $\mathbf{X}_1$ and $\mathbf{X}_2$, we are now using $A$ and $B$. We find this generally more readable, and particularly simplifies the notation in Section 4.2. 
	\item At the end of Section 4.1, we have rewritten the likelihood function in terms of the agreement patterns and the summary statistics. This is the text added:

	This likelihood is then used throughout Section 4.2 in the discussion of efficient posterior inference. We hope this expression clarifies the meaning of "preservation of weight (Comment 5), and strengthens the argument for $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{N} \}$ being summary statistics for $\bm{m}$, $\bm{u}$, and $\bm{Z}$ (Comment 4).

@@

	\item To denote when the $(i,j)$ record pair exhibits agreement pattern $p$, we have removed the clunky $(i, j) \in h_p$ notation for $\gamma_{ij} = h_p$, which we feel is more direct and intuitive.

	\item In Section 4.1, we have provided a specific example of a comparison vector and how the hashing procedure works.

	\item Section 4.1 introduces the summary statistic $N_{j_p}$. After careful review, we realized that by changing the order of subscripts and instead using $N_{p_j}$, we can replace the sum of counts across all records (previously denoted $H_p$), with the more intuitive $N_p$. Thus, we have removed all of the ''$H$" quantities throughout Section 4. We believe this substantially improves readability. 
\end{itemize}
}

\pointRaised{AE}{Line 80 on p. 3 says: “For ease of readability, we follow the convention established by Sadinle (2017) and say “record $i \in X_1$” rather than the more compact $x_{1i}$.” Taking this at face value implies that, in any sentence, one could swap “record $i \in X_1$” for “$x_{1i}$,” which clearly is not true.  So, as it stands, the sentence does little to improve ease of readability.  In fact, if the point is that “$x_{1i}$” will never be used again, why is the notation introduced in the first place?}

\reply{We added this sentence in an attempt to address a previous reviewer comment pointing out a conflation between the record itself and the index directing towards that record. We did in fact intend for “record $i \in X1$” to be mean precisely $x_1i$. However, we see now that introducing $x_{1i}$ has introduced new confusion. With the simplified reference to the two datasets as $A$ and $B$, that material now reads:

@@

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{% 
		The assumption is missing completely at random. You are correct that this is a result of the independence assumed across elements of the comparison vector. This has been clarified.
	}

	\pointRaised{R}{%
	Appendix 8.2: I appreciate the streamlining of the discussion of the proposed algorithms and think it was a good choice to move the full derivation to an appendix. However, I do not follow the re-expression of the pmf for $\Gamma_{.j}$. First, the opening square brackets are still misplaced
	throughout. In the second line of this derivation, the authors divide the expression by a product of the element-wise conditional probabilities of a match in the comparison vector (u), raised by an indicator that the element of the comparison vector equals a particular value. Perhaps I misunderstand, but I believe this product is not constant in $\Gamma_{.j}$ or $u$, and so the total expression is not proportional to the line above, as interpreted as a pmf. I think that the end effect is that the last line of the newly expressed pmf is missing a factor of $\prod_i \prod_f \prod_l u_{fl}^{I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}$ regardless of the value of $z_j$.}

\reply{%
	The square brackets have been corrected, and we apologize for the oversight. We have also prepared an alternative derivation of the likelihood for $Z_j$, separately handling the case when $B_j$ has a match and when it does not. We believe this is more clear. 
}

@@

	\pointRaised{R}{%
Appendix 8.2: Thank you for including the details on integrating out pi from the full conditionals. They surprised me. I had assumed that the authors had integrated out pi in the prior for Z, as this is what Sadinle (2017) had done to form the “beta prior for bipartite matchings”. Does the alternate approach presented in this paper provide a different algorithm than directly integrating the prior distribution? Is the presented alternative approach justified?}

\reply{%
	The reviewer raises important questions. The main difference between the full conditionals in Sadinle (2017) and ours is that for him, $Z$ is a partition, while for us, it is not. This is what required him to integrate out $\pi$ in the prior, and then sequentially update each component of the $Z$ vector.

	The approach we have is justified, as indicated in the proof provided. However, under closer review, we have determined that it is unnecessary. Without integrating out $\pi$, all paramaters are updated through a standard Gibbs sampler. Furthermore, in other work we are developing, we actually need samples of $\pi$ in different applications.

	We reran all case studies and simulation using samples of $\pi$ in the full conditional for $Z$, and found no difference in results. This is unsurprising, because with high numbers of observations, the posterior of the beta distribution is highly concentrated around its mean.

@@

	Therefore, we have updated the paper with full conditionals for the standard Gibbs sampler. We leave the remark about marginalization in the Appendix to highlight the similarity to Sadinle's method.

}

\pointRaised{R}{%
	I do not understand the statement just below Equation (10): “When j has no match in $X_1$, we write $(n_1 +j, j) \in h_{P+1}$” My understanding of these patterns is that they are based on observed comparison vectors without consideration of Z (matches). In the second paragraph of Section 4.3, the H notation includes the matches (Z), in notation and definition that seems to conflict with the statement just below Equation (10). This also comes into play in Equation (16)}

	\reply{%
	You are correct that the comparison vectors are created (and therefore, patterns are assigned) without regard to $Z$. This notation was created purely to be able to denote when a record was left unlinked during the Gibbs Sampler as in Equation 16 in the submitted draft.

@@

	I can see why this is confusing. Therefore, I have removed that line, and changed the notation for record $B_j$ being unmatched to just be''otherwise".
	}

\pointRaised{R}{%
	Third paragraph of Section 4.1: The authors claim they are computing “sufficient statistics”. What exactly are these statistics sufficient for?
	}

	\reply{%
		We show in the revised Section 4.2 that the perspective of patterns allows us to write conditional likelihoods  and posterior updates for $\bm{m}$, $\bm{u}$, and $\bm{Z}$ entirely throught the statistics in $\tilde{\Gamma} = \{\mathcal{P}, \mathcal{R}, \mathcal{N} \}$. However, we cannot express the full likelihood in (14) through these statistics. Therefore, we have revised to text to say ``summary statistics" instead of the more technical ``sufficient statistics."}

@@

\pointRaised{R}{%
	First paragraph of Section 4.2: The authors state: “Posterior calculations still attribute the appropriate weight to all records through the summary statistics…” What is meant by the term “weight”? Which records are appropriately weighted – those in X2?}

\reply{%

	We have switched the order of Sections 4.2 and 4.3, so that we first discuss hashing, then posterior inference, then chunkwise computation of the comparison matrix, and then SEI. With this new ordering, and with the newlyu provided equations (15 -19) it is clearer that the contribution of \emph{all} record pairs is recorded through the summary statistics in $\mathcal{N}$.
}

@@

\pointRaised{R}{%
	Second paragraph of Section 4.2: “and delete those comparison vectors”. Which are “those” vectors?}

\reply{%
	We have revised that sentence to read ''We then conduct hashing, obtain the compressed $\tilde{\Gamma}^{ab}$ for later calculations, and delete the larger $\Gamma^{ab}$ from memory before continuing with the next chunk of data."
}

\pointRaised{R}{%
	Where does $R^{SEI, cd}$ come into play in the partitioned algorithm presented in Equations (13) and (14)? I recommend that the authors either refrain from suppressing the SEI notation or further explain how the SEI algorithm has changed the quantities in these equations.}

\reply{%
	We have reordered Section 4 so that all posterior inference is presented before SEI. This makes it clear that the posterior updates in (16a), (16b), and (18) depend only on $\mathcal{N}$. SEI only affects the step shown in (19). We have provided an additional simulation study to show robustness to the SEI procedure. 
}

@@

\pointRaised{R}{%
	Section 4.2: I appreciate the practical advice about choosing S for the SEI method. However, this choice seems arbitrary in the absence of further discussion/evidence. Given that the primary novelty of the manuscript is in methods to speed and otherwise improve computation, I am surprised that this aspect of computational innovation is presented with virtually no theoretical or empirical exploration. Presumably the SEI method has some sort of accuracy trade-off, as the authors warn that linkage results may be “distorted” if S is low. However, this trade-off is not quantified or even discussed in practical terms beyond the terse recommendation to choose S=10.
}

\reply{% 
	We have provided an additional simulation study in Section 5.3 to show robustness to different choices of $S$.
}
\pointRaised{R}{%
	Page 5, 2 sentences before equation (4): I believe the sum should be of $I(Z_j \leq n_1)$, not $I(Z_j \leq n_1 +1)$.}

@@

\pointRaised{R}{%
	Equation (6a): The indices do not match the subscripts in the indicator function in each summand, or their standard meaning in table 1.}

\reply{%
	This has been fixed.
}

\pointRaised{R}{%
	Generally, the authors seem to arbitrarily use upper and lower case z interchangeably in function definitions.}

\reply{%
	We use $Z$ when discussing a random quantity, and $z$ to reference a realized value. We have revised, and have found all instances of inconsistency. 
}

@@

\pointRaised{R}{%
Equations (8) and (9): Should the weights have superscript (s) (as the Zs do)?}

\reply{%
	This has been fixed. 
}

\pointRaised{R}{%
	Gamma is in some places described as a set and in others as a matrix (particularly in sections 4.2 and 5.1).
}

\reply{%
	$\gamma$ is a matrix comprised by comparison vectors. It is certainly not a set in the mathematical sense. All references to $\gamma$ as a set have been removed.
}

### 2023-07-07 ba_resubmit/kundinger_resubmit2.tex
updated draft

\usepackage{lineno}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\newtheorem{lemma}{Lemma}
\usepackage{booktabs}       % professional-quality tables
\usepackage{algorithm}      % algorithm environment
\usepackage{algpseudocode}

@@

In many data analysis tasks, analysts seek to identify duplicate records across two data files. This is an increasingly important task in ``data cleaning'' and is used for inferential and predictive analyses in fields such as statistics, computer science, machine learning, political science, economics, precision medicine, official statistics, and others \citep{christen_2012, gutman2013bayesian, DalzellReiter18, tang2020}. In this article, we consider bipartite record linkage, which merges two data files that contain duplications across, but not within, the respective data files.

@@

Consider two data files $A$ and $B$, consisting of records $A_i$ and $B_j$ respectively, where $i \in \{1, \ldots n_A\}$ and $j \in \{1, \ldots n_B\}$. Without loss of generality, denote files such that $n_A \geq n_B$. Under bipartite matching, the set of matches across data files can be represented in two equivalent ways. First, we may use a matrix $\Delta \in \{0, 1\}^{n_A \times n_B}$, where
\begin{align}
	\Delta_{ij} =
	\begin{cases}
		1, & \text{if records}\;  A_i \; \text{and}\; B_j \; \text{refer to the same entity}; \\
		0, & \text{otherwise}.\\
	\end{cases}
\end{align}
This sparse matrix representation can become cumbersome for large linkage tasks. More compactly, bipartite matching also can be viewed as a labeling $\bm{Z} = (Z_1, \ldots, Z_{n_B})$ for the records in $B$ such that 
\begin{align}
	Z_{j} =
	\begin{cases}
		i, & \text{if records}\;  A_i \; \text{and}\; B_j  \; \text{refer to the same entity}; \\
		n_A + j, & \text{if record}\;  B_j \; \text{does not have a match in}\; A. \\
	\end{cases}
\end{align}
We can go back and forth between the two using $\Delta_{ij} = I(Z_j = i),$ where $I(\cdot) = 1$ when the expression inside the parentheses is true, and $I(\cdot) = 0$ otherwise.

Denote the set of matches by $\bm{M} = \{(i,j): \Delta_{ij} = 1\}$, and the set of non-matches by 
$\bm{U} =  \{(i,j): \Delta_{ij} = 0\}.$ The record linkage task can be viewed as identifying  $\bm{M}$ and  $\bm{U}.$ We refer to record pairs that are estimated as matches as ``links'' and to record pairs that are estimated as non-matches as ``non-links.''

@@

Intuitively, matching records (those that refer to the same entity) should be similar; records that are non-matching should be dissimilar. \cite{fellegi_theory_1969} proposed encoding this using a comparison vector $\bm{\gamma}_{ij}$ computed for each record pair $(i,j)$ in $A \times B.$ Denote the number of criteria for comparing records by $F$, such that $\gamma_{ij} = (\gamma_{ij}^1, \ldots, \gamma_{ij}^F).$ We collect the vectors $\bm{\gamma}_{ij}$ as the comparison matrix $\Gamma \in \mathbb{R}^{n_A n_B \times F}$.

%Frequently, $\bm{\gamma}_{ij}$ consists of one comparison for each feature shared between the two data files.

@@

{\color{red}{
In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data. To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise.}
}

@@

The seminal \cite{fellegi_theory_1969} model employs two independence assumptions: first, that comparison vectors are conditionally independent given their matching status, and second, that the matching status of the record pairs are independent. Using these assumptions, \cite{winkler_state_1999, jaro1989, larsen_2001, enamorado2019using} and others model the comparison data through mixture models of the form
\begin{subequations}
\begin{align}
	&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 1 \stackrel{iid}{\sim} \mathcal{M}(\bm{m}), \label{eqn:fs_model} \\
	&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 0  \stackrel{iid}{\sim} \mathcal{U}(\bm{u}), \label{eqn:m_dist}\\
	&\Delta_{ij}   \stackrel{iid}{\sim} \text{Bernoulli}(\lambda). \label{eqn:u_dist}
\end{align}
\end{subequations}
Here, $\mathcal{M}$ and $\mathcal{U}$ are the distributions for matching and non-matching record pairs, $\bm{m}$ and $\bm{u}$ are their respective sets of parameters, and $\lambda$ is the marginal probability that a record pair is a match. When using comparison vectors with discrete agreement levels, $\mathcal{M}$ and $\mathcal{U}$ are collections of independent multinomial distributions for each linkage feature. Accordingly, $\bm{m} = (\bm{m}_1, \ldots, \bm{m}_F)$, where $\bm{m}_f = (m_{f1}, \ldots, m_{fL_f})$ and $m_{fl} = P(\gamma_{ij}^f = l|\Delta_{ij} = 1)$ for all fields $f$ and agreement levels $l$. The $\bm{u}$ parameters are defined similarly, with $u_{fl} = P(\gamma_{ij}^f = l|\Delta_{ij} = 0)$.

@@

%The comparison data $\bm{\gamma}_{ij}$ are not sufficient to determine whether a record is a match or non-match because of errors that naturally occur in the data. This motivated \cite{fellegi_theory_1969} to consider the likelihood ratio
%\begin{align}
%	\label{eqn:wts}
%	w_{ij} = \frac{P(\gamma_{ij} \mid \Delta_{ij} = 1)}{P(\gamma_{ij} \mid \Delta_{ij} = 0)}
%\end{align}
%as a weight to estimate if record pairs are a match or non-match. This ratio will be large when there is strong evidence of the pair being a match, and small otherwise. 
%
%In practice, $P(\cdot \mid \Delta_{ij} = 1)$ and $P(\cdot \mid \Delta_{ij} = 0)$ are unknown to the modeler, and thus must be estimated. 
%
%%is the set of parameters $u_{fl} = P(\gamma_{ij}^f = l|Z_j \neq i)$ for the non-matching pairs.
%
%After estimating $\bm{m}$ and $\bm{u}$, the Fellegi-Sunter method uses thresholds $T_m$ and $T_u$ such that all record pairs with $w_{ij} > T_m$ are declared as links, and all those with $w_{ij} < T_u$ are declared as non-links (with those such that $T_u < w_{ij} < T_m$ left undetermined and subject to clerical review). This is a problem in practice as transitive closures can be violated. Since each $w_{ij}$ is calculated independently, there can be situations in which both $w_{ij} > T_m$ and $w_{i'j} > T_m$, so both $(i,j)$ and $(i, j')$ are declared as links, even though such a matching is not allowed by assumption.

@@

To estimate a one-to-one matching without using a post-processing step, \cite{sadinle_bayesian_2017} incorporates this constraint directly into the model through a Bayesian framework. In addition to standard Dirichlet priors for the $\bm{m}_f$ and $\bm{u}_f$ parameters, he proposes the ``beta distribution for bipartite matching" for the linkage parameter $\bm{Z}$. He assigns a prior distribution for the probability of the indicator that a record in $B$ has a match in $A$, so that $I(Z_j \leq n_A) \sim \text{Bernoulli}(\pi)$, where $\pi$ itself is taken to be distributed $\text{Beta}(\alpha_{\pi}, \beta_{\pi})$. It follows that the number of records in $B$ that have matches, denoted $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B} I(Z_j \leq n_A)$, is distributed according to a $\text{Beta-Binomial}(n_B, \alpha_{\pi}, \beta_{\pi})$. Conditioning on the set of records in $B$ that have matches, formally denoted $\{I(Z_j \leq n_A)\}_{j=1}^{n_B}$, all $n_A ! / (n_A - n_{AB}(\bm{Z}))!$ bipartite matchings are taken to be equally likely. Thus, the beta distribution for bipartite matching, is given by
\begin{align}
\label{eqn:sadinle_prior}
P(\bm{Z}|\alpha_{\pi}, \beta_{\pi}) = \frac{(n_A - n_{AB}(\bm{Z}))!}{n_A !}\frac{\text{B}(n_{AB}(\bm{Z}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}) + \beta_{\pi})}{\text{B}(\alpha_{\pi}, \beta_{\pi})},
\end{align}
where $\text{B}(\cdot, \cdot)$ represents the Beta function. This prior strictly enforces one-to-one matching, inducing a Gibbs sampler that removes previously matched records from the set of candidate records when sampling each $Z_j$. This makes the sampler inherently serial, which can be slow when working on linkage tasks with more than a few thousand records.

%hyperparameters $\alpha_{\pi}$ and $\beta_{\pi}$ encode prior beliefs about the proportion of records in $B$ that have matches in $\bm{X_1}$, and $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B} I(Z_j \leq n_A + j)$ is the number of records in $B$ that have a match in $A$. 
%One criticism of the independent matching assumption is that the decision rule leads to ``many-to-many assignments,'' breaking one-to-one matching assumptions. One way of resolving this issue to incorporate the constraint directly into the model as follows:
%\begin{align}
%	&\bm{\Gamma}_{ij} \mid Z_j =i \stackrel{iid}{\sim} \mathcal{M}(\bm{m}),  \\
%	&\bm{\Gamma}_{ij} \mid Z_j \neq i \stackrel{iid}{\sim} \mathcal{U}(\bm{u}) \notag, \\
%	& \bm{Z} \sim \mathcal{B}, \notag
%\end{align}
%where $\mathcal{B}$ represents a prior on the space of bipartite matchings, and $\mathcal{M}(\bm{m})$ and $\mathcal{U}(\bm{u})$ are models for the comparison vectors of matches and non-matches. For \texttt{BRL}, \cite{sadinle_bayesian_2017} proposed the beta distribution for bipartite matching, given by
%$$P(\bm{Z}|\alpha_{\pi}, \beta_{\pi}) = \frac{(n_A - n_{AB}(\bm{Z}))!}{n_A !}\frac{\text{B}(n_{AB}(\bm{Z}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}) - \beta_{\pi})}{\text{B}(\alpha_{\pi}, \beta_{\pi})},
%$$
%where $\text{B}(\cdot, \cdot)$ represents the Beta function, hyperparameters $\alpha_{\pi}$ and $\beta_{\pi}$ encode prior beliefs about the proportion of records in $\bm{X_2}$ that have matches in $\bm{X_1}$, and $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B} I(Z_j \leq n_A + j)$ is the records in $B$ that have a match in $A$. This prior induces a Gibbs sampler that strictly enforces one-to-one matching, removing previously matched records from the set of candidate records when sampling $Z_j$. This creates a dependency that makes the sampler inherently serial, which can slow down the sampler when working on large linkage tasks.

@@

In contrast to the prior over the vector $\bm{Z}$ from \cite{sadinle_bayesian_2017}, we follow \cite{wortman2019} and use independent priors for each component $Z_j$. However, unlike \cite{wortman2019} who proposes a flat prior for $Z_j$, we use a proper prior. We denote the fast Beta prior as follows. For each $Z_j$, we have
\begin{align}
	\label{eqn:fast_beta_prior}
	p(Z_j = z_j| \pi) &= \begin{cases} 
	\frac{1}{n_A}\pi,  & z_j \leq n_A; \\
	1-\pi, &  z_j  = n_A + j; \\
\end{cases} \\
\pi &\sim \text{Beta}(\alpha_{\pi}, \beta_{\pi}) \notag.
\end{align}
We can interpret (\ref{eqn:fast_beta_prior}) as follows: record $B_j$ has some match in $A$ with probability $\pi$, and each record $A_i$ is equally likely to be that match. The hyperparameters $\alpha_{\pi}$ and $\beta_{\pi}$ encode prior beliefs about  the proportion of records in $B$ that have matches in $A.$

@@

To obtain an estimate $\hat{\bm{Z}}$ of the linkage structure, we use the loss functions and Bayes estimate from \cite{sadinle_bayesian_2017}. Since the prior does not strictly enforce one-to-one matching, it is possible for this Bayes estimate to link multiple records in $B$ to one record in $A$. To achieve a Bayes estimate that fulfills the one-to-one matching requirement, we minimize the expected loss subject to the constraint that $\hat{Z}_j \neq \hat{Z}_{j'}$ for all $j \neq j'$. Details for the initial Bayes estimate and the post-processing procedure are provided in Appendix \ref{bayes-estimate}.

>>>>

\usepackage{lineno}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\newtheorem{lemma}{Lemma}
\usepackage{booktabs}       % professional-quality tables
\usepackage{algorithm}      % algorithm environment
\usepackage{algpseudocode}
\usepackage{subcaption}

@@

Before conducting data analysis, it is often necessary to identify duplicate records across two data files. This is an increasingly important task in ``data cleaning'' and is used for inferential and predictive analyses in fields such as statistics, computer science, machine learning, political science, economics, precision medicine, official statistics, and others \citep{christen_2012, gutman2013bayesian, DalzellReiter18, tang2020}. In this article, we consider bipartite record linkage, which merges two data files that contain duplications across, but not within, the respective data files.

@@

Consider two data files $A$ and $B$, consisting of records $\{A_i: i = 1, \ldots, n_A\}$ and $\{B_j: j = 1, \ldots, n_B\}$. Suppose the files have $F$ fields in common to be used for linkage, and that these fields take on values $A_{if}$ and $B_{jf}$ respectively. Without loss of generality, denote files such that $n_A \geq n_B$. Under bipartite matching, the set of matches across data files can be represented in two equivalent ways. First, we may use a matrix $\Delta \in \{0, 1\}^{n_A \times n_B}$, where
\begin{align}
	\Delta_{ij} =
	\begin{cases}
		1, & \text{if records}\;  A_i \; \text{and}\; B_j \; \text{refer to the same entity}; \\
		0, & \text{otherwise}.\\
	\end{cases}
\end{align}
This sparse matrix representation can become cumbersome for large linkage tasks. More compactly, bipartite matching also can be viewed as a labeling $\bm{Z} = (Z_1, \ldots, Z_{n_B})$ for the records in $B$ such that 
\begin{align}
	Z_{j} =
	\begin{cases}
		i, & \text{if records}\;  A_i \; \text{and}\; B_j  \; \text{refer to the same entity}; \\
		n_A + j, & \text{if record}\;  B_j \; \text{does not have a match in}\; A. \\
	\end{cases}
\end{align}
We can go back and forth between the two using $\Delta_{ij} = I(Z_j = i),$ where $I(\cdot) = 1$ when the expression inside the parentheses is true, and $I(\cdot) = 0$ otherwise.

{\color{red}{The following paragraph is pretty unnecessary, I never use this notation}}
Denote the set of matches by $\bm{M} = \{(i,j): i \leq n_A, j \leq n_B, \Delta_{ij} = 1\}$, and the set of non-matches by 
$\bm{U} =  \{(i,j): i \leq n_A, j \leq n_B, \Delta_{ij} = 0\}.$ The record linkage task can be viewed as identifying  $\bm{M}$ and  $\bm{U}.$ We refer to record pairs that are estimated as matches as ``links'' and to record pairs that are estimated as non-matches as ``non-links.''

@@

{\color{red}{Beka suggested eliminating the following two paragraphs. Thoughts? I think the first one is good, the second seems unneccesary.}}

Intuitively, matching records (those that refer to the same entity) should be similar; records that are non-matching should be dissimilar. \cite{fellegi_theory_1969} proposed encoding this using a comparison vector $\gamma_{ij}$ computed for each record pair $(i,j)$ in $A \times B.$ Denote the number of criteria for comparing records by $F$, such that $\gamma_{ij} = (\gamma_{ij}^1, \ldots, \gamma_{ij}^F).$ {\color{red}{We use $\Gamma_{ij}$ when referring to the vector as a random variable, and $\gamma_{ij}$ when referring to observed data. We collect the vectors $\gamma_{ij}$ as the comparison matrix $\gamma \in \mathbb{R}^{n_A n_B \times F}$}}.

%Frequently, $\gamma_{ij}$ consists of one comparison for each feature shared between the two data files.

@@

{\color{red}{
In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data. }
}

@@

The seminal \cite{fellegi_theory_1969} model employs two independence assumptions: first, that comparison vectors are conditionally independent given their matching status, and second, that the matching status of the record pairs are independent. Using these assumptions, \cite{winkler_state_1999}, \cite{jaro1989}, \cite{larsen_2001}, \cite{enamorado2019using} and others model the comparison data through mixture models of the form
\begin{subequations}
\begin{align}
	&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 1 \stackrel{iid}{\sim} \mathcal{M}(\bm{m}), \label{eqn:fs_model} \\
	&\Gamma_{ij} = \gamma_{ij} \mid \Delta_{ij} = 0  \stackrel{iid}{\sim} \mathcal{U}(\bm{u}), \label{eqn:m_dist}\\
	&\Delta_{ij}   \stackrel{iid}{\sim} \text{Bernoulli}(\lambda). \label{eqn:u_dist}
\end{align}
\end{subequations}
Here, $\mathcal{M}$ and $\mathcal{U}$ are the distributions for matching and non-matching record pairs, $\bm{m}$ and $\bm{u}$ are their respective sets of parameters, and $\lambda$ is the marginal probability that a record pair is a match. When using comparison vectors with discrete agreement levels, $\mathcal{M}$ and $\mathcal{U}$ are collections of independent multinomial distributions for each linkage feature. Accordingly, $\bm{m} = (\bm{m}_1, \ldots, \bm{m}_F)$, where $\bm{m}_f = (m_{f1}, \ldots, m_{fL_f})$ and $m_{fl} = P(\gamma_{ij}^f = l|\Delta_{ij} = 1)$ for all fields $f$ and agreement levels $l$. The $\bm{u}$ parameters are defined similarly, with $u_{fl} = P(\gamma_{ij}^f = l|\Delta_{ij} = 0)$.

@@

%The comparison data $\gamma_{ij}$ are not sufficient to determine whether a record is a match or non-match because of errors that naturally occur in the data. This motivated \cite{fellegi_theory_1969} to consider the likelihood ratio
%\begin{align}
%	\label{eqn:wts}
%	w_{ij} = \frac{P(\gamma_{ij} \mid \Delta_{ij} = 1)}{P(\gamma_{ij} \mid \Delta_{ij} = 0)}
%\end{align}
%as a weight to estimate if record pairs are a match or non-match. This ratio will be large when there is strong evidence of the pair being a match, and small otherwise. 
%
%In practice, $P(\cdot \mid \Delta_{ij} = 1)$ and $P(\cdot \mid \Delta_{ij} = 0)$ are unknown to the modeler, and thus must be estimated. 
%
%%is the set of parameters $u_{fl} = P(\gamma_{ij}^f = l|Z_j \neq i)$ for the non-matching pairs.
%
%After estimating $\bm{m}$ and $\bm{u}$, the Fellegi-Sunter method uses thresholds $T_m$ and $T_u$ such that all record pairs with $w_{ij} > T_m$ are declared as links, and all those with $w_{ij} < T_u$ are declared as non-links (with those such that $T_u < w_{ij} < T_m$ left undetermined and subject to clerical review). This is a problem in practice as transitive closures can be violated. Since each $w_{ij}$ is calculated independently, there can be situations in which both $w_{ij} > T_m$ and $w_{i'j} > T_m$, so both $(i,j)$ and $(i, j')$ are declared as links, even though such a matching is not allowed by assumption.

@@

To estimate a one-to-one matching without using a post-processing step, \cite{sadinle_bayesian_2017} incorporates this constraint directly into the model through a Bayesian framework. In addition to {\color{red}{uniform}} Dirichlet priors for the $\bm{m}_f$ and $\bm{u}_f$ parameters, he proposes the ``beta distribution for bipartite matching" for the linkage parameter $\bm{Z}$. He assigns a prior distribution for the probability of the indicator that a record in $B$ has a match in $A$, so that $I(Z_j \leq n_A) \sim \text{Bernoulli}(\pi)$, where $\pi$ itself is taken to be distributed $\text{Beta}(\alpha_{\pi}, \beta_{\pi})$. It follows that the number of records in $B$ that have matches, denoted $n_{AB}(\bm{Z}) = \sum_{j=1}^{n_B} I(Z_j \leq n_A)$, is distributed according to a $\text{Beta-Binomial}(n_B, \alpha_{\pi}, \beta_{\pi})$. Conditioning on the set of records in $B$ that have matches, formally denoted $\{I(Z_j \leq n_A)\}_{j=1}^{n_B}$, all $n_A ! / (n_A - n_{AB}(\bm{Z}))!$ bipartite matchings are taken to be equally likely. Thus, the prior is given by
\begin{align}
\label{eqn:sadinle_prior}
P(\bm{Z}|\alpha_{\pi}, \beta_{\pi}) = \frac{(n_A - n_{AB}(\bm{Z}))!}{n_A !}\frac{\text{B}(n_{AB}(\bm{Z}) + \alpha_{\pi}, n_B - n_{AB}(\bm{Z}) + \beta_{\pi})}{\text{B}(\alpha_{\pi}, \beta_{\pi})},
\end{align}
where $\text{B}(\cdot, \cdot)$ represents the Beta function. This prior strictly enforces one-to-one matching, inducing a Gibbs sampler that removes previously matched records from the set of candidate records when sampling each $Z_j$. This makes the sampler inherently serial, which can be slow when working on linkage tasks with more than a few thousand records.

@@

In contrast to the prior over the vector $\bm{Z}$ from \cite{sadinle_bayesian_2017}, we follow \cite{wortman2019} and use independent priors for each component $Z_j$. However, unlike \cite{wortman2019} who proposes a flat prior for $Z_j$, we use the fast Beta prior as follows. For each $Z_j$, we have
\begin{align}
	\label{eqn:fast_beta_prior}
	p(Z_j = q| \pi) &= \begin{cases} 
	\frac{1}{n_A}\pi,  & q \leq n_A; \\
	1-\pi, &  q  = n_A + j; \\
\end{cases} \\
\pi &\sim \text{Beta}(\alpha_{\pi}, \beta_{\pi}) \notag.
\end{align}
We can interpret (\ref{eqn:fast_beta_prior}) as follows: record $B_j$ has some match in $A$ with probability $\pi$, and each record $A_i$ is equally likely to be that match. The hyperparameters $\alpha_{\pi}$ and $\beta_{\pi}$ encode prior beliefs about  the proportion of records in $B$ that have matches in $A.$

@@

To obtain an estimate $\hat{\bm{Z}}$ of the linkage structure, we use the loss functions and Bayes estimate from \cite{sadinle_bayesian_2017}. However, there is a crucial difference: since \ref{eqn:fast_beta_prior} does not strictly enforce one-to-one matching, it is possible for this Bayes estimate to link multiple records in $B$ to one record in $A$. To achieve a Bayes estimate that fulfills the one-to-one matching requirement, we minimize the expected loss subject to the constraint that $\hat{Z}_j \neq \hat{Z}_{j'}$ for all $j \neq j'$. Details for the initial Bayes estimate and the post-processing procedure are provided in Appendix \ref{bayes-estimate}.

\begin{table}[t!]
	\centering
	\begin{tabular}[t!]{ll}
		Symbol & Description \\
		\hline
		$A, B$ & data files\\
		$i \in 1, \ldots, n_A $ & index over records in $A$\\
		$j \in 1, \ldots, n_B $ & index over records in $B$\\
		$f \in 1, \ldots F$ & index over fields used for comparisons \\
		$l \in 1, \ldots L_f$ & index over agreement levels for feature $f$ \\
		$n_{AB}$ & number of entities in common between $A$ and $B$\\
		$\gamma_{ij}$ & comparison vector for records $A_i$ and $B_j$ \\
		$Z_j = i$ & records $A_i$ and $B_j$ match \\
		$Z_j = n_A + j$ & record $B_j$ has no match in $A$ \\
		$m_{fl}$ & $P(\gamma_{ij}^f = l | Z_j = i)$ \\
		$u_{fl}$ & $P(\gamma_{ij}^f = l | Z_j \neq i)$ \\
		$\pi$ & probability that a record in $B$ has a match in $A$ \\
		\hline
	\end{tabular}\caption{Summary of model notation.}\label{table_notation_A}
\end{table}
